%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior software engineer} % Job title
    {Self-employed} % Organization
    {Worldwide} % Location
    {Feb. 2015 --- PRESENT} % Date(s)
    {    
    Currently working remotely on a Java trading platform in a small firm. Other notable projects:
      \begin{cvitems}
      \item{Writing software developments articles on a personal website: \cvhref{http://foat.me}{foat.me}. It mostly includes Scala articles.}
      \item{Wrote a book in the fields of computer vision and web development: \cvcite{foat2015cv_web}.}
      \item{Designed and implemented robust and fast algorithm for multiply chalkboard detection. It works in real-time and processes more than 40 HD images per second on a regular computer. The pixel precision is higher than 90\%.}
      \item{Created a Java throttling framework from scratch using Spring MVC and AspectJ.}
      \end{cvitems}
      Related skills: Scala, Java, DevOps, Unit testing, Mocking, Aspects, TDD, BDD, JavaScript, C++, Spring Framework, Play framework, OpenCV, Build automation tools, Git, Computer vision, Image processing.
    }
    
%---------------------------------------------------------
  \cventry
    {Computer vision researcher} % Job title
    {\cvhref{http://cmp.felk.cvut.cz}{Center for Machine Perception}} % Organization
    {Prague, Czech Republic} % Location
    {Nov. 2014 --- Jan. 2015} % Date(s)
    {
	Worked as a researcher and developer on a project in the field of \textit{Image rectification using vanishing lines and local affine frames}. Notable achievements:
      \begin{cvitems}
      \item{Designed and developed a line-annotation tool on Matlab.}
      \item{Created a test system for vanishing points and lines detection algorithms using C++ and Matlab.}
      \item{Improved existing vanishing points detection algorithm.}
      \end{cvitems}
      Related skills: C++, Matlab, Unix, Git, Computer vision, Image processing.
    }
    
%---------------------------------------------------------
  \cventry
    {Computer vision developer} % Job title
    {\cvhref{http://roadar.ru}{RoadAR}} % Organization
    {Kazan, Russia} % Location
    {Jul. 2013 --- Sep. 2014} % Date(s)
    {
    Worked on a \cvhref{https://play.google.com/store/apps/details?id=ru.roadar.android}{RoadAR project}. The application warns drivers about traffic-signs and other necessary information. Notable achievements:
      \begin{cvitems}
      \item{Created a novel algorithm for traffic-sign detection and recognition, which works in real-time on mobile phones. The algorithm showed a superior performance compared to many state-of-the-art approaches. The algorithm is implemented on C++.}
      \item{Designed a test system using Java for the traffic-sign detection algorithm.}
      \end{cvitems}
      Related skills: C++, Java, OpenCV, Unit testing, PostgreSQL, Swing, Maven, Android NDK, Boost library, CMake, Git, Computer vision, Image processing, Machine learning.
    }
    
%---------------------------------------------------------
  \cventry
    {Senior software engineer} % Job title
    {\cvhref{http://dz.ru}{Digital Zone}} % Organization
    {Kazan, Russia} % Location
    {Apr. 2013 --- Jul. 2013} % Date(s)
    {
      \begin{cvitems_up}
      \item{Managed a small team on a mobile version of \cvhref{http://m.ulmart.ru}{m.ulmart.ru} website.}
      \item{Conducted technical interviews.}
      \end{cvitems_up}
      Related skills: Java, MySQL, Spring MVC, Apache Solr, JavaScript, Application servers, Freemarker, Git, Maven.
    }

%---------------------------------------------------------
  \cventry
    {Software developer} % Job title
    {\cvhref{http://dz.ru}{Digital Zone}} % Organization
    {Kazan, Russia} % Location
    {Sep. 2011 --- Apr. 2013} % Date(s)
    {
    Developed complex services for several high-loaded websites. Mostly worked on \cvhref{http://www.ulmart.ru}{ulmart.ru} project. Notable achievements related to this website:
      \begin{cvitems}          
      \item{Built a search platform based on Apache Solr.}
      \item{Created an asynchronous catalog of goods using JavaScript and Spring MVC.}
      \item{Designed and implemented a new database. This helped to remove several bottlenecks and improve the website performance.}
      \end{cvitems}
	Related skills: Java, GWT, DevOps, Spring MVC, MySQL, EJB, Apache Solr, JavaScript, Application servers, Freemarker, Version control, Build automation tools.
    }
%---------------------------------------------------------
\end{cventries}
