\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}
\usepackage{fontawesome}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{color}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=0.8]{Monaco}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

\def\myauthor{Foat Akhmadeev}
\def\mytitle{\myauthor - vita}
\def\myphone{+1 (773) 828-4272}
\def\myemail{foat.akhmadeev@gmail.com}
\def\mygithub{github.com/foat}
\def\mylinkedin{linkedin.com/in/akhmadeevfoat}
\def\myhomesite{foat.me}
\def\mycitizenship{Russia}
\def\mytimezone{UTC+3}

\usepackage[bookmarks, colorlinks, breaklinks,
	pdftitle={\myauthor - vita},
	pdfauthor={\myauthor}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\LARGE \myauthor}\\[1cm]
\begin{minipage}[t]{2in}
\flushleft {Scala/Java software engineer}
\end{minipage}
\begin{minipage}[t]{2in}
\flushleft
\faHome \, \href{http://\myhomesite}{\myhomesite}\\
\faEnvelope \, \href{mailto:\myemail}{\myemail}\\
\faPhone \, \myphone\\
\faGithub \, \href{https://\mygithub}{\mygithub}\\
\faLinkedin \, \href{https://\mylinkedin}{\mylinkedin}\\
\end{minipage}
\begin{minipage}[t]{3in}
\flushleft
\textbf{citizenship} \, \mycitizenship\\
\textbf{time zone}\, \, \, \mytimezone\\
\end{minipage}

\section*{Interests}
Software engineering • Project management • Computer vision \\
Scala • E-commerce • Writing

\section*{Professional experience}
\noindent
\years{2015-present}{Self-employed, \textbf{Senior software engineer}
\begin{itemize}
\item{Java, Scala, C++ development.}
\item{Computer vision R\&D.}
\item{Project management.}
\item{Projects:
\begin{itemize}
\item{A website development using Scala Play framework.}
\item{Java throttling framework development from scratch.}
\item{Robust and fast algorithm for multiply chalkboard detection.}
\item{Real-time road lane recognition on C++.}
\item{Book writing in fields of web development and computer vision: \cite{foat2015cv_web}.}
\item{Working on a financial project (Java).}
\end{itemize}
}
\item{Related skills: Scala, Java, Unit testing, Mocking, TDD, BDD, JavaScript, C++, Spring Framework, Play framework,
OpenCV, Build automation tools, Git.}
\end{itemize}
\years{2014-2015}{\href{http://cmp.felk.cvut.cz}{CMP}, \textbf{Computer vision researcher}
\begin{itemize}
\item{Computer vision R\&D.}
\item{Project: Image rectification using vanishing lines and local affine frames.}
\item{Related skills: C++, Matlab, Unix, Git.}
\end{itemize}
\years{2013-2014}{\href{http://roadar.ru}{RoadAR}, \textbf{Computer vision developer}
\begin{itemize}
\item{Computer vision R\&D.}
\item{Real-time traffic sign recognition on mobile phones.}
\item{Project: \href{https://play.google.com/store/apps/details?id=ru.roadar.android}{RoadAR}}.
\item{Related skills: C++, Java, OpenCV, Unit testing, PostgreSQL, Swing, Maven, Android NDK, Boost library, CMake, Git.}
\end{itemize}
}
\years{2013}{\href{http://dz.ru}{Digital Zone}, \textbf{Senior software developer}
\begin{itemize}
\item{Project management and code review.}
\item{Conducting technical interviews.}
\item{Java frontend and backend development.}
\item{Project: \href{http://www.ulmart.ru}{ulmart.ru} (\href{http://dz.ru/portfolio/clients/ulmart/release_1-0/}{link 1}, \href{http://dz.ru/portfolio/clients/ulmart/release_2-0/}{link 2}).}
\item{Related skills: Java, MySQL, Spring MVC, Apache Solr, JavaScript, Application servers, Freemarker, Git, Maven.}
\end{itemize}
}
\years{2011-2013}{\href{http://dz.ru}{Digital Zone}, \textbf{Software developer}
\begin{itemize}
\item{Java frontend and backend development.}
\item{Projects:
\begin{itemize}
\item{Social networks related websites.}
\item{\href{http://www.ulmart.ru}{ulmart.ru}}.
\end{itemize}
}
\item{Related skills: Java, GWT, Spring MVC, EJB, Apache Solr, JavaScript, Application servers, Freemarker, Version control, Build automation tools.}
\end{itemize}
}

\section*{Education}
\noindent
\years{2012-2014}{\textbf{MSc in Computer Science}\\
\textit{Kazan Federal University}, Russia\\
\textsc{advisor}: Evgeny Stolov, Kazan Federal University
\begin{itemize}
\item{Computer vision, Image processing.}
\item{Project: \textit{3D scene reconstruction from a single view}. Publication: \cite{foat2014prediction}}.
\item{Related skills: Matlab, C++, \TeX}.
\end{itemize}
}
\years{2008-2012}{\textbf{BSc in Computer Science}\\
\textit{Kazan Federal University}, Russia\\
\textsc{advisors}: Evgeny Stolov, Kazan Federal University; Aleksandr Shlyannikov, Kazan Federal University
\begin{itemize}
\item{Computer vision, Image processing, Web development.}
\item{Projects: \textit{Handwritten digit recognition}, \textit{E-library using GWT}}.
\item{Related skills: Java, JEE, GWT}.
\end{itemize}
}

\section*{It \& programming skills}
\textit{Main languages}: Java, Scala, C++.\\
\textit{Data analysis}: Matlab.\\
\textit{Scripting languages}: Shell script, JavaScript.\\
\textit{Markup languages}: XML, JSON, HTML, CSS.\\
\textit{Query languages}: SQL.\\
\textit{Application and web servers}: JBoss, Tomcat, Jetty.\\
\textit{Revision control}: Git, Subversion.\\
\textit{Build tools}: Maven, Gradle, CMake, SBT.\\
\textit{Systems on administration level}: OS X, Linux.\\
\textit{Other}: Spring Framework, Play framework, OpenCV, Swing, Android NDK, MySQL, PostgreSQL, TDD, BDD.\\
\textit{Digital typesetting}: \TeX, \LaTeX.

\section*{Languages}
\textit{Russian} (native speaker),\\
\textit{English} (professional proficiency).

\renewcommand{\refname}{\section*{Publications}}
\bibliographystyle{IEEEtran}
\bibliography{lib}

\vfill{}

\begin{center}
{\scriptsize  Last updated: \today\- •\-
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
\fontspec{Times New Roman}Lua\TeX}\\
\href{https://foat.me/cv.pdf}{https://foat.me/cv.pdf}}
\end{center}

\end{document}
